On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-02-02 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt

Response for Referee #1
---

1. (p. 1, L17-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon. We kindly note that GMVR is an iterative regression method that works for equally spaced grids, and constructs rational functions (equivalently, sums of rational functions) that smoothly connect or interpolate data assuming a rational ansatz.

2. (p. 1, L32) Thank you. We have added the citation.

3. (p. 1, L44) We have added this reference.

4. (p. 1, L46) We have kept only Leaver's reference at this line. There are indeed many many publications that could be cited here, but Leaver's is one of the earliest and most relevant.

5. (p. 1, L52) We have altered the language here to not mention the topic of completeness.

6. (Third Paragraph) We now no longer constrain this discussion to n=0. The text has been modified to include updated references and now state (perhaps uninformatively) that all phenom models have high frequency regions that are consistent with perturbation theory.

7. (p. 1, L49-50) Thank you. We hope that the current text will avoid any confusion.

8. (p. 1, L52-53) Thank you. We hope that the current text will avoid any confusion.

9. (p. 2, L30) Thank you. We hope that the current text will avoid any confusion.

10. (p. 2, L30) Thank you. We agree that Yang+ should be referenced here.

11. (p. 2, L39)

### 2019-02-02 docs/mvfits_paper/mvf.tex
intermediate update prior to resubmission

During this period, a few to dozens of \bbh{} signals are likely to be detected \cite{Abbott:2016nhf}.

@@

These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature \cite{Leaver85,London:2014cma}.

@@

The well known and effective completeness of these solutions allows \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin weight -2 spheroidal harmonics, $_{-2}S\lmn$.

@@

This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered, and ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.

@@

The consequences of that approximation, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,Berti:2014fga,London:2018gaq}.

@@

This approximation also applies to many of the \textit{Phenom} models, where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.

@@

\par Both Phenom and \eob{} approaches directly use phenomenological models for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.

@@

While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature (e.g. \cite{Berti:2005ys,Berti:2014fga}), there exist minor shortcomings which we wish to address here.

@@

\par For the \qnm{} frequencies, it is well known that for nearly extremal \bh{s} (i.e. $\jf \rightarrow 1$) some of the frequencies have zero-damping (i.e. $\tau\lmn \rightarrow \infty$) \cite{Zimmerman:2015trm}.

@@

In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.

@@

Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping in the extremal Kerr limit.

@@

\par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.

@@

As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.

@@

In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).

@@

For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.

>>>>

During this period, a few to dozens of \bbh{} signals are likely to be detected \cite{Abbott:2016nhf,Abbott2018OS}.

@@

These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature \cite{Leaver85}.

@@

These solutions allow \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin weight -2 spheroidal harmonics, $_{-2}S\lmn$.

@@

This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.

@@

The consequences of that approximation, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,Berti:2014fga,London:2018gaq,Kelly:2012nd}.

@@

This approximation also applies to the \textit{Phenom} models,
where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain

@@

\cite{ Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq, Khan:2018fmp }.
\par Both Phenom and \eob{} approaches either use phenomenological models of remnant \bh{} mass and spin to interpolate over tables of \qnm{} frequencies, or phenomenological models for \qnm{} frequencies are used directly.
Either approach typically incurs less computational cost that the direct numerical calculation of \qnm{} frequencies, which may involve, for example, the solving of continued fraction equations \cite{Leaver85}.

@@

While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature (e.g. \cite{Berti:2005ys, Berti:2014fga, Cook:2014cta}), there exist minor shortcomings which we wish to address here.

@@

\par For both the \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.

@@

This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin \cite{Husa:2015iqa,London:2018gaq}.

@@

\par For the \qnm{} frequencies, it is well known that for nearly extremal \bh{s} (i.e. $\jf \rightarrow 1$) some of the frequencies have zero-damping (i.e. $\tau\lmn \rightarrow \infty$) \cite{Yang:2012pj,Zimmerman:2015trm}.

@@

In the context of \gw{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.

@@

Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping \textit{and} non-zero-damping in the extremal Kerr limit.

@@

% \par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
% As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.
% In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).
% For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.

@@

\par For the modeling of $\sigma\LMlmn$, we note that the \cite{Berti:2014fga} do not appear to include the \qnm{s} which rotate counter to the \bh{} spin direction (i.e. ``mirror-modes'').
In addition to our
